RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-12-19 introduction.tex
notes

>>>>

\carlos{General plan: we take Kandel et al.'s interview study, and Heer and Agrawala design considerations, and make them integral to the explanation of RCloud, throughout the whole paper.}

\carlos{We need to remake all the figures, pretty much. They need to have real notebooks, on each and every one of them.}

\carlos{Update with new RCloud features. Multiple languages, full-text searching, shiny, ...}

### 2014-12-19 relatedwork.tex
notes

\begin{figure}
\includegraphics[width=\linewidth]{fig/system/system.pdf}
\caption{\label{fig:system}A diagram of RCloud's architecture. Dashed
  lines represent features which not yet implemented.}
\end{figure}

@@

>>>>

\begin{figure}
\includegraphics[width=\linewidth]{fig/system/system.pdf}
\caption{\label{fig:system}A diagram of RCloud's architecture. Dashed
  lines represent features which not yet implemented. \carlos{Must remove anything that isn't implemented}}
\end{figure}

@@

\carlos{There's no need to position ourselves defensively here; we're
  addressing different needs, and the connection is already
  tenuous. We're just hurting ourselves by comparing to wrangling and
  then saying ``well, we don't have wrangling''}

### 2014-12-19 system.tex
yes
notes

% High-level architecture

@@

\subsection{System Design}

@@

\subsection{Executing R in a web browser\label{sec:executinginbrowser}}

@@

>>>>

\subsection{High-level Architecture\label{sec:highlevelarchitecture}}

@@

\subsection{Human Interface\label{sec:humaninterface}}

@@

\subsection{Executing R in a web browser\label{sec:Rinbrowser}}

@@

\carlos{In-depth explanation of R<->web interconnect, and why it's
  necessary or important. Main point: make programming in the R side
  as close as possible to what R programming feels like, and make
  programming in the Javascript side as close as possible to what
  Javascript programming feels like. We do this because this part of
  the system is targeted at programmers; Shiny targets web programming
  at non-web-programmers. We don't attempt such a thing and land at a
  different point in the spectrum.}
